The Quantum Internet

### 2020-09-01 Sections/quality_of_service.tex
almost done editing.

\section{Quality of service}\index{Quantum error correction (QEC)}\index{Quality of service (QoS)}\label{sec:QOS_chap}

@@

\subsection{Entanglement purification}\index{Entanglement!Purification}

As we will later see in Sec.~\ref{sec:ent_ultimate}, Bell pairs are a ubiquitous resource for many quantum information processing applications, and warrant special treatment in their own right.

Entanglement purification (or distillation) is a process by which two imperfect distributed Bell pairs can be condensed into a single Bell pair of higher quality (as measured by a fidelity metric, Sec.~\ref{sec:fid_metric}).

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob. Let us assume a bit-flip error model in this instance\footnote{The same protocol can be employed to correct against phase-flip errors by operating in a Hadamard-rotated basis.}, in which case the imperfect Bell pairs are of the form,
\begin{align}
\hat\rho^F_{A,B} &= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\hat{X}_1\ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \nonumber \\
&= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\ket{\Psi^+}\bra{\Psi^+},
\end{align}
That is, we have a mixture of,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B + \ket{1}_A\ket{1}_B),	
\end{align}
with probability $F$, and,
\begin{align}
\ket{\Psi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B + \ket{1}_A\ket{0}_B),	
\end{align}
with probability \mbox{$1-F$}. The goal is to `filter' out the latter of these.
x 
Alice and Bob then perform their entanglement purification protocol -- operations to reduce them to a single Bell pair of higher fidelity,
\begin{align}
\mathcal{E}_\mathrm{purif}(\hat\rho^{F_\mathrm{in}}_{A,B} \otimes \hat\rho^{F_\mathrm{in}}_{A,B}) \to \hat\rho^{F_\mathrm{out}}_{A,B},
\end{align}
where,
\begin{align}
F_\mathrm{out}>F_\mathrm{in}.
\end{align}

The purification process $\mathcal{E}_\mathrm{purif}$ is realised very simply by Alice and Bob both performing parity measurements\index{Bell!Measurements} on their two qubits, whose measurement outcomes indicate whether the two qubits were equal ($+$) or different ($-$) -- their parity. These are easily implemented using CNOT gates, using the construction shown in Fig.~\ref{fig:parity_meas}, which implement the projectors,
\begin{align}\index{Bell!Measurements}\index{Parity!Projectors}
\hat\Pi^+ &= \ket{0,0}\bra{0,0} + \ket{1,1}\bra{1,1}, \nonumber \\
\hat\Pi^- &= \ket{0,1}\bra{0,1} + \ket{1,0}\bra{1,0}.
\end{align}

They complete the protocol by classically communicating their measurement outcomes, and performing appropriate local corrections.

\begin{figure}[!htbp]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{} & \qw & \targ & \meter \\
		\lstick{} & \qw & \ctrl{-1} & \qw
		} \nonumber
	\end{align}
	\captionspacefig \caption{Construction of a parity measurement circuit using a single CNOT gate and a single-qubit measurement. The measurement outcome indicates whether the two input qubits were the same (\mbox{$\ket{0}\ket{0}$}, \mbox{$\ket{1}\ket{1}$}) or different (\mbox{$\ket{0}\ket{1}$}, \mbox{$\ket{1}\ket{0}$}). See Sec.~\ref{sec:bell_proj} for a simple linear optics construction for this operation.}\label{fig:parity_meas}\index{Bell!Measurements}
\end{figure}

Two such parity projections project a 4-qubit state down to a 2-qubit state. The full circuit for this entanglement purification protocol is shown in Fig.~\ref{fig:ent_purif_circ}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.39\textwidth]{entanglement_purification}
\captionspacefig \caption{Protocol for entanglement purification of two noisy Bell pairs (blue) into a single less noisy Bell pair. Not shown are trivial single-qubit local corrections that may need to be made, depending upon measurement outcomes.} \label{fig:ent_purif_circ}\index{Entanglement!Purification}
\end{figure}

Let us illustrate the operation of the circuit by example of different possible input states.

Suppose there were no errors, the ideal case. Then the input state was,
\begin{align}
\ket\psi_\mathrm{in} &= \ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4}\\
&= \frac{1}{2}(\ket{0}_1\ket{0}_2+\ket{1}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Upon parity measurement we obtain,
\begin{align}
\hat\Pi^+_{1,3} \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},
\end{align}
and we obtain the desired output Bell pair (with an $\hat{X}$ correction in the case of the odd-parity outcome).

Note that if both qubits from one Bell pair are subject to bit-flips, this is equivalent to no error, since,
\begin{align}
	\hat{X}_1\hat{X}_2\ket{\Phi^+}_{1,2}=\ket{\Phi^+}_{1,2}.
\end{align}

Now suppose there was a bit-flip error on the first qubit of the first pair. Now the input state is,
\begin{align}
\ket\psi_\mathrm{in} &= \hat{X}_1 \ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4}\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Now upon parity measurement we obtain,
\begin{align}
\hat\Pi^+_{1,3} \hat{X}_1\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \hat{X}_1\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},
\end{align}
and following correction we achieve a bit-flipped Bell pair.

Finally, with both Bell pairs subject to a single bit-flip,
\begin{align}
\ket\psi_\mathrm{in} &= \hat{X}_1\hat{X}_3 \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} \\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{1}_3\ket{0}_4+\ket{0}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the parity measurement,
\begin{align}
\hat\Pi^+_{1,3} \hat{X}_1\hat{X}_3\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},\nonumber \\
\hat\Pi^-_{1,3} \hat{X}_1\hat{X}_3\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},
\end{align}
recovering the expected Bell pair, without an erroneous bit-flip.

Evidently, the output Bell pair is subject to an unexpected bit-flip iff one of the Bell pairs was subject to a bit-flip error. This yields the output fidelity,
\begin{align}
F_\mathrm{out} = \frac{{F_\mathrm{in}}^2}{{F_\mathrm{in}}^2 + (1-F_\mathrm{in})^2},
\end{align}
and thus the purification protocol improves fidelity provided that \mbox{$F_\mathrm{out}>F_\mathrm{in}$}, which implies the input fidelity must satisfy \mbox{$F_\mathrm{in}>1/2$}.

>>>>

\section{Error correction}\index{Quantum error correction (QEC)}\index{Quality of service (QoS)}\label{sec:QOS_chap}

@@

%\subsection{Entanglement purification}\index{Entanglement!Purification}
%
%As we will later see in Sec.~\ref{sec:ent_ultimate}, Bell pairs are a ubiquitous resource for many quantum information processing applications, and warrant special treatment in their own right.
%
%Entanglement purification (or distillation) is a process by which two imperfect distributed Bell pairs can be condensed into a single Bell pair of higher quality (as measured by a fidelity metric, Sec.~\ref{sec:fid_metric}).
%
%More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob. Let us assume a bit-flip error model in this instance\footnote{The same protocol can be employed to correct against phase-flip errors by operating in a Hadamard-rotated basis.}, in which case the imperfect Bell pairs are of the form,
%\begin{align}
%\hat\rho^F_{A,B} &= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\hat{X}_1\ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \nonumber \\
%&= F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\ket{\Psi^+}\bra{\Psi^+},
%\end{align}
%That is, we have a mixture of,
%\begin{align}
%\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B + \ket{1}_A\ket{1}_B),	
%\end{align}
%with probability $F$, and,
%\begin{align}
%\ket{\Psi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B + \ket{1}_A\ket{0}_B),	
%\end{align}
%with probability \mbox{$1-F$}. The goal is to `filter' out the latter of these.
%x 
%Alice and Bob then perform their entanglement purification protocol -- operations to reduce them to a single Bell pair of higher fidelity,
%\begin{align}
%\mathcal{E}_\mathrm{purif}(\hat\rho^{F_\mathrm{in}}_{A,B} \otimes \hat\rho^{F_\mathrm{in}}_{A,B}) \to \hat\rho^{F_\mathrm{out}}_{A,B},
%\end{align}
%where,
%\begin{align}
%F_\mathrm{out}>F_\mathrm{in}.
%\end{align}
%
%The purification process $\mathcal{E}_\mathrm{purif}$ is realised very simply by Alice and Bob both performing parity measurements\index{Bell!Measurements} on their two qubits, whose measurement outcomes indicate whether the two qubits were equal ($+$) or different ($-$) -- their parity. These are easily implemented using CNOT gates, using the construction shown in Fig.~\ref{fig:parity_meas}, which implement the projectors,
%\begin{align}\index{Bell!Measurements}\index{Parity!Projectors}
%\hat\Pi^+ &= \ket{0,0}\bra{0,0} + \ket{1,1}\bra{1,1}, \nonumber \\
%\hat\Pi^- &= \ket{0,1}\bra{0,1} + \ket{1,0}\bra{1,0}.
%\end{align}
%
%They complete the protocol by classically communicating their measurement outcomes, and performing appropriate local corrections.
%
%\begin{figure}[!htbp]
%	\begin{align}
%		\Qcircuit @C=.7em @R=.4em @! {
%		\lstick{} & \qw & \targ & \meter \\
%		\lstick{} & \qw & \ctrl{-1} & \qw
%		} \nonumber
%	\end{align}
%	\captionspacefig \caption{Construction of a parity measurement circuit using a single CNOT gate and a single-qubit measurement. The measurement outcome indicates whether the two input qubits were the same (\mbox{$\ket{0}\ket{0}$}, \mbox{$\ket{1}\ket{1}$}) or different (\mbox{$\ket{0}\ket{1}$}, \mbox{$\ket{1}\ket{0}$}). See Sec.~\ref{sec:bell_proj} for a simple linear optics construction for this operation.}\label{fig:parity_meas}\index{Bell!Measurements}
%\end{figure}
%
%Two such parity projections project a 4-qubit state down to a 2-qubit state. The full circuit for this entanglement purification protocol is shown in Fig.~\ref{fig:ent_purif_circ}.
%
%\begin{figure}[!htbp]
%\includegraphics[clip=true, width=0.39\textwidth]{entanglement_purification}
%\captionspacefig \caption{Protocol for entanglement purification of two noisy Bell pairs (blue) into a single less noisy Bell pair. Not shown are trivial single-qubit local corrections that may need to be made, depending upon measurement outcomes.} \label{fig:ent_purif_circ}\index{Entanglement!Purification}
%\end{figure}
%
%Let us illustrate the operation of the circuit by example of different possible input states.
%
%Suppose there were no errors, the ideal case. Then the input state was,
%\begin{align}
%\ket\psi_\mathrm{in} &= \ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4}\\
%&= \frac{1}{2}(\ket{0}_1\ket{0}_2+\ket{1}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
%\end{align}
%Upon parity measurement we obtain,
%\begin{align}
%\hat\Pi^+_{1,3} \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},\nonumber \\
%\hat\Pi^-_{1,3} \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},
%\end{align}
%and we obtain the desired output Bell pair (with an $\hat{X}$ correction in the case of the odd-parity outcome).
%
%Note that if both qubits from one Bell pair are subject to bit-flips, this is equivalent to no error, since,
%\begin{align}
%	\hat{X}_1\hat{X}_2\ket{\Phi^+}_{1,2}=\ket{\Phi^+}_{1,2}.
%\end{align}
%
%Now suppose there was a bit-flip error on the first qubit of the first pair. Now the input state is,
%\begin{align}
%\ket\psi_\mathrm{in} &= \hat{X}_1 \ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4}\\
%&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
%\end{align}
%Now upon parity measurement we obtain,
%\begin{align}
%\hat\Pi^+_{1,3} \hat{X}_1\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},\nonumber \\
%\hat\Pi^-_{1,3} \hat{X}_1\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},
%\end{align}
%and following correction we achieve a bit-flipped Bell pair.
%
%Finally, with both Bell pairs subject to a single bit-flip,
%\begin{align}
%\ket\psi_\mathrm{in} &= \hat{X}_1\hat{X}_3 \ket{\Phi^+}_{1,2}\ket{\Phi^+}_{3,4} \\
%&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{1}_3\ket{0}_4+\ket{0}_3\ket{1}_4).\nonumber
%\end{align}
%Upon performing the parity measurement,
%\begin{align}
%\hat\Pi^+_{1,3} \hat{X}_1\hat{X}_3\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \ket{\Phi^+}_{2,4},\nonumber \\
%\hat\Pi^-_{1,3} \hat{X}_1\hat{X}_3\ket{\Phi^+}_{1,2} \ket{\Phi^+}_{3,4} &= \hat{X}_2\ket{\Phi^+}_{2,4},
%\end{align}
%recovering the expected Bell pair, without an erroneous bit-flip.
%
%Evidently, the output Bell pair is subject to an unexpected bit-flip iff one of the Bell pairs was subject to a bit-flip error. This yields the output fidelity,
%\begin{align}
%F_\mathrm{out} = \frac{{F_\mathrm{in}}^2}{{F_\mathrm{in}}^2 + (1-F_\mathrm{in})^2},
%\end{align}
%and thus the purification protocol improves fidelity provided that \mbox{$F_\mathrm{out}>F_\mathrm{in}$}, which implies the input fidelity must satisfy \mbox{$F_\mathrm{in}>1/2$}.

### 2020-09-01 cambridge.tex
almost done editing.

% The Quantum Internet - A New Frontier
% Peter P. Rohde et al.

% Publication mode:
%   0 = Draft (figures disabled, quicker compiling)
%   1 = Preprint (for Red Pen of Death - Dowling's eyes only)
%   2 = Two-column article
%   3 = Single-column book

% Sketches/serious mode:
%	0 = off
%	1 = on

% Set numbers here

\def\pubmode{2}
\def\sketchesmode{0}
\def\seriousmode{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%

\if 0\pubmode % Draft mode (figures disabled)
	\documentclass[draft, twocolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-2}
	\let\stdsection\section
	\renewcommand\section{\newpage\stdsection}
\fi

\if 1\pubmode % Preprint (Dowling's eyes only)
	\documentclass[preprint, aps, rmp, singlecolumn, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-2}
\fi

\if 2\pubmode % Two-column article
	\documentclass[twocolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-2}
\fi

\if 3\pubmode % Single-column book
	\documentclass[singlecolumn, aps, rmp, amsmath, amssymb, nofootinbib, superscriptaddress, longbibliography, floatfix, table-of-contents, eqsecnum]{revtex4-2}
	\let\stdpart\part
	\renewcommand\part{\newpage\stdpart}
\fi

\input{Sections/packages}

\input{Sections/commands_and_definitions}

\hypersetup{
	pdfauthor = {Peter P. Rohde et al.},
	pdftitle = {The Quantum Internet -- A New Frontier},
	pdfsubject = {Quantum Internet},
	pdfkeywords = {Quantum, Computing, Networks, Internet}
}

\makenomenclature
\makeindex

\begin{document}

%
% Pre-matter
%

\title{\huge{The Quantum Internet --- A New Frontier}\\ \large{\QIhomepage}}

\input{Sections/authors}

\date{\today}

\frenchspacing

\input{Sections/abstract}

\maketitle

\input{Sections/dedication}

\input{Sections/table_of_contents}

\sketch{sketch_1}

@@

\if 0\seriousmode
	\input{Sections/mission_statement}
\fi

@@

\input{Sections/quantum_internet_project}

@@

\part{Mathematical foundations}\label{part:mathematical_foundations}\index{Mathematical foundations}

\input{Sections/mathematical_foundations}
\input{Sections/intro_to_QM}
\input{Sections/intro_to_QO}
\input{Sections/intro_to_QIT}

@@

\input{Sections/QTCP}

\latinquote{O derint dum metuant.}

\input{Sections/QTCP_protocol_stack}

\latinquote{Divide et impera.}

\input{Sections/collision_handling_and_classical_errors}

\latinquote{Esse est percipi.}

\input{Sections/multi_packet_operations}

\latinquote{Capax infiniti.}

\input{Sections/extensibility_of_QTCP}

\latinquote{Cedere nescio.}

\input{Sections/scalability_of_QTCP}

\famousquote{Beware of bugs in the above code. I have only proved it correct, not tried it.}{Donald Knuth}

\input{Sections/quality_of_service}

@@

\part{Entanglement distribution}\label{part:ent_dist}
\index{Entanglement!Distribution}

@@

\latinquote{Acta deos numquam mortalia fallunt.}

@@

\clearpage

%
% State of the art
%

\part{History \& state-of-the-art}\label{part:SotA}\index{State-of-the-art}\index{History}

\input{Sections/state_of_the_art}

\sketch{sketch_12}

\clearpage

%
% To the future & beyond
%

\part{To the future \& beyond}\label{part:future_beyond}

\input{Sections/to_the_future_and_beyond}

\latinquote{Excelsior.}

\input{Sections/the_quantum_space_race}

\latinquote{Volens et potens.}

\input{Sections/quantum_genetic_medicine}

\latinquote{Annus mirabilis.}

\input{Sections/the_quantum_mind}

\latinquote{Grandescunt aucta labore.}

%\input{Sections/quantum_biology}

\input{Sections/optimising_the_world}

\latinquote{Ceteris paribus.}

\sketch{sketch_13}

%
% Roadmap - The way forward
%

\input{Sections/roadmap}

\latinquote{Aut inveniam viam aut faciam.}

\sketch{sketch_14}

%
% Essays - A New Frontier
%

\part{Essays -- A new frontier}\label{part:essays}\label{part:essays}\index{Essays}\index{A new frontier}

@@

\input{Sections/how_to_learn_more}

\if 0\seriousmode
	\input{Sections/epilogue}
\fi

\latinquote{Opus dei.}

\input{Sections/acknowledgements}

\latinquote{Dum spiro, spero.}

\input{Sections/statement_of_contributions}

\input{Sections/list_of_abbreviations}

\if 0\seriousmode
	\input{Sections/wine_pairings}
\fi

\bibliography{quantum_internet, nana_ML}

\input{Sections/index}

\input{Sections/about_the_authors}

\sketch{sketch_final}

\famousquote{We all die. The goal isn't to live forever, the goal is to create something that will.}{Chuck Palahniuk}

>>>>

%\NeedsTeXFormat{LaTeX2e}[1996/06/01]

\documentclass[multi,spanningrule]{cambridge6A}

\def\authorpage{0}
\def\abstractpage{0}
\def\dedicationpage{0}
\def\sketchesmode{0} 	
\def\seriousmode{1} 			
\def\maincontribstyle{0}
\def\QIPlink{0}
\def\parainTOC{0}
\def\includelicense{0}
\def\doublecol{0}

\input{Sections/packages}
\input{Sections/commands_and_definitions}

  \usepackage{natbib}

  \usepackage{rotating}
  \usepackage{floatpag}
  \rotfloatpagestyle{empty}

 %\usepackage{amsmath}
 %  \usepackage{amsthm}
 % \usepackage{graphicx}

% for a single index
% \usepackage{makeidx}
 \makeindex

 \newcommand\cambridge{cambridge6A}

  \setcounter{tocdepth}{2}% the toc normally lists sections;
% for the purposes of this document, this has been extended to subsections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \includeonly{chap1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{document}

  \title[]{The Quantum Internet}

  \author{Peter P. Rohde}

  \frontmatter
  \maketitle
  \tableofcontents
 % \listoffigures
 % \listoftables
  \listofcontributors

  \mainmatter

@@

@@

%\input{Sections/quantum_internet_project}

@@

%\part{Mathematical foundations}\label{part:mathematical_foundations}\index{Mathematical foundations}

%\input{Sections/mathematical_foundations}
%\input{Sections/intro_to_QM}
%\input{Sections/intro_to_QO}
%\input{Sections/intro_to_QIT}

@@

@@

\part{Entanglement distribution}\label{part:ent_dist}\index{Entanglement!Distribution}

@@

%\latinquote{Acta deos numquam mortalia fallunt.}

%\input{Sections/quality_of_service}

@@

\clearpage
%
%%
%% To the future & beyond
%%
%
%\part{To the future \& beyond}\label{part:future_beyond}
%
%\input{Sections/to_the_future_and_beyond}
%
%\latinquote{Excelsior.}
%
%\input{Sections/the_quantum_space_race}
%
%\latinquote{Volens et potens.}
%
%\input{Sections/quantum_genetic_medicine}
%
%\latinquote{Annus mirabilis.}
%
%\input{Sections/the_quantum_mind}
%
%\latinquote{Grandescunt aucta labore.}
%
%%\input{Sections/quantum_biology}
%
%\input{Sections/optimising_the_world}
%
%\latinquote{Ceteris paribus.}
%
%\sketch{sketch_13}
%
%%
%% Roadmap - The way forward
%%
%
%\input{Sections/roadmap}
%
%\latinquote{Aut inveniam viam aut faciam.}
%
%\sketch{sketch_14}
%
%
% Essays - A New Frontier
%

\part{Essays}\label{part:essays}\label{part:essays}\index{Essays}\index{A new frontier}

@@

%
%\input{Sections/how_to_learn_more}
%
%\if 0\seriousmode
%	\input{Sections/epilogue}
%\fi
%
%\latinquote{Opus dei.}
%
%\input{Sections/acknowledgements}
%
%\latinquote{Dum spiro, spero.}
%
%\input{Sections/statement_of_contributions}
%
%\input{Sections/list_of_abbreviations}
%

\bibliography{quantum_internet, nana_ML}
\bibliographystyle{cambridgeauthordate}

%
%\input{Sections/index}
%
%%\input{Sections/about_the_authors}
%
%\sketch{sketch_final}
%
%\famousquote{We all die. The goal isn't to live forever, the goal is to create something that will.}{Chuck Palahniuk}
%

  \backmatter

  \addtocontents{toc}{\vspace{\baselineskip}}
  \theendnotes

  \cleardoublepage

\printindex
